---
title: "Introduction to Data Science - HW 2"
author: "Renato Silva e Silva - `rsilvaesilva1664@floridapoly.edu`"
output: html_notebook
---

# Problem 1 (30 points)

During class you completed an activity in which you practiced `git` commands and operations (such as forking a repository, cloning it using `git clone`, and uploading changes using `git push`).

In this exercise you are asked to modify the `flpoly_student.md` file you worked during class, and format it using the **markdown** tools discussed in class. You must **create a table** that shows the courses you are currently enrolled in, using for the headers of the table: 

- Prefix: in bold letters (such as **COP**)
- Number: in bold letters (such as **2073**)
- Name: in italics (such as _Introduction to Data Science_)
- Credits (such as 3)

a. Make sure your GitHub repo (`practice-repo/`) shows the results of your updated file (remember to use the commands `git add .` , `git commit -m "YOUR MESSAGE"`, and `git push`) 

b. Include a link to your GitHub repo in this document.
[Link to Github](https://github.com/sturtevantgrace/practice-repo/blob/main/flpoly_student.md)

c. Take a screenshot of the GitHub repo, add the screenshot file to the repo, and include it in this document (review how to insert a picture using markdown)
[Class Table Screenshot](https://github.com/sturtevantgrace/practice-repo/blob/main/Class%20Table.png)

# Problem 2 (30 points)

For this problem, you are asked to create a list of **3 concepts** you have learned about so far this semester. Include the name of the course as a sub-heading (that is, using `##`), and the concepts as an unordered list. Include a link to information about at least one of the concept you listed (for example a link to the Wikipedia page about that concept/topics).

# Concepts learned this semster 
## Calculus 
- [limits](https://en.wikipedia.org/wiki/Limit_%28mathematics%29)
- [derivatives](https://en.wikipedia.org/wiki/Derivative)

## Data Sceicne
- [how to code is R](https://en.wikipedia.org/wiki/RStudio)



# Problem 3 (40 points)

In this problem you will practice some basic R operations. Include solutions to each items by inserting a new R chunk of code (make sure you run the chunk so that the output is displayed)

(a) Create a variable called `my_name` that contains your preferred name.

```{r}
make_full_name <- function(first_name, last_name) {
  full_name <- paste(first_name, last_name)
  full_name
}
my_name <- make_full_name("Renato", "Silva e Silva")
print(my_name)
```

(b) Create a variable called `name_length` that holds how many letters are in `my_name`.

```{r}
name_length <- nchar(my_name)
print(name_length)
```

(c) Show which value is bigger: $e^\pi$ or $\pi^e$. 

```{r}
e <-  2.71875
e^pi > pi^e
# e^pi is bigger because the string returns true
````

(d) Define a function called `add_three` that takes a single argument and returns a value with 3 units added to the original input.

```{r}
add_three <- round(3.28376489 + 3)
print(add_three)

```

(e) Use the colon operator `:` to create a vector `v` of numbers from 10 to 49. Find the length of this vector using the `length()` function.

```{r}
vector <- 10:49
length(vector)
```

(f) Use the `seq()` function to produce a range of number from -5 to 10 in 0.5 increments.

```{r}
seq(-5, 10, 0.5)
```


